Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-06-18 ms.tex
repeating smoothing experiment without going through source aperture.

@@

\subsection{Cryogenic Vacuum (CV) Stability Tests}

>>>>

The dramatic difference from the smoothing kernel is beyond what is possible for a real source.
This is because the 40 pixel wide kernel was applied all the way through the source aperture, which would subtract and distort any signal from a star/planet source.
In reality, the kernel should be wider than the source aperture diameter and interpolate through the source points.
We repeated the experiment with a 161 pixel wide kernel and masked bad pixels and the source pixels.
\textcolor{red}{\bf Continue Here!}

@@

\subsection{Goddard Cryogenic Vacuum (CV) Stability Tests}
